Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-10-21 reviews.Rmd
references still does not work

---
title          : "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
authors        : "Aaron Peikert, Maximilian S. Ernst & Andreas M. Brandmaier"
journal        : "Meta-Psychology"
manuscript-id  : "4139"
cutout-quotes  : true
class          : "draft"
output         : papaja::revision_letter_pdf
manuscript-src : manuscript.Rmd
bibliography   : references.bib
---

>>>>

---
title          : "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
authors        : "Aaron Peikert, Maximilian S. Ernst & Andreas M. Brandmaier"
journal        : "Meta-Psychology"
manuscript-id  : "4139"
cutout-quotes  : true
class          : "draft"
output         : papaja::revision_letter_pdf
manuscript-src : manuscript.Rmd
---
